% !TEX program = xelatex
% !TEX root = xelatex_main.tex
\chapter{实现内核里的全局同步}

CUDA没有内核里的全局同步，这和CUDA的思想是格格不如的。
\begin{itemize}
\item 全局同步开销很贵
\item 不同硬件有不同的运算核，代码应该
\item 自己的
\item At the block level, allows blocks to be executed in any order on GPUCan use different sizes of blocks depending upon the resources of GPU – so-called “transparent scalability”
\end{itemize}

但是这不见得是不能实现的。\cite{conf/ipps/XiaoF10}

最后以这样一段来结束本章：

While code.accelerate@gmail.com makes every effort to present accurate and reliable information in this chapter, code.accelerate@gmail.com does not endorse, approve, or certify such information, nor does it guarantee the accuracy, completeness, efficiency, timeliness, or correct sequencing of such information.   Use of such information is voluntary, and reliance on it should only be undertaken after an independent review of its accuracy, completeness, efficiency, and timeliness.  Reference herein to any specific commercial product, process, or service by trade name, trademark, service mark, manufacturer, or otherwise does not constitute or imply endorsement, recommendation, or favoring by code.accelerate@gmail.com.

code.accelerate@gmail.com assumes no responsibility for consequences resulting from the use of the information herein, or from use of the information obtained in this chapter, or in any respect for the content of such information, including (but not limited to ) errors or omissions, the accuracy or reasonableness of factual or scientific assumptions, studies or conclusions, the defamatory nature of statements, ownership of copyright or other intellectual property rights, and the violation of property, privacy, or personal rights of others.  code.accelerate@gmail.com is not responsible for, and expressly disclaims all liability for, damages of any kind arising out of use, reference to, or reliance on such information.  No guarantees or warranties, including (but not limited to) any express or implied warranties of merchantability or fitness for a particular use or purpose, are made by code.accelerate@gmail.com with respect to such information.
